### 2020-10-04 manuscript/paper_BRM.Rmd
some figure layout changes

authornote: |
  We would like to thank Daan van Renswoude and Maartje Raijmakers for their helpful comments on earlier versions of this paper. Furthermore, we would like to acknowledge feedback by Karel Veldkamp and Phil Norberts in the early stage of this project.

@@

keywords          : "eye movements; eye-tracking; parameter recovery; dependent mixture models"
wordcount         : "8861"

@@

print(plots.rmsd.234[[1]][[1]] + coord_flip())

@@

print(plots.rmsd.234[[1]][[2]] + coord_flip())

@@

print(plots.rmsd.234[[1]][[3]] + coord_flip())

>>>>

authornote: |
  We would like to thank Daan van Renswoude, Maartje Raijmakers, and Maximilian Maier for their helpful comments on earlier versions of this paper. Furthermore, we would like to acknowledge feedback by Karel Veldkamp and Phil Norberts in the early stage of this project.

@@

keywords          : "eye movements; eye-tracking; parameter recovery; dependent mixture models"
wordcount         : "9605"

@@

print(plots.rmsd.234[[1]][[1]] + coord_flip() + theme(axis.text.x = element_text(size = 10)))

@@

print(plots.rmsd.234[[1]][[2]] + coord_flip() + theme(axis.text.x = element_text(size = 8)))

@@

print(plots.rmsd.234[[1]][[3]] + coord_flip() + theme(axis.text.x = element_text(size = 9)))
